---
title: "hw3_P8105_hr2569"
author: "Hongzhu Ren"
date: "2023-10-11"
output: github_document
---
```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
```

# Problem 1
```{r instacart_import}
data("instacart")
```
This dataset contains `r nrow(instacart)` data of `r ncol(instacart)` variables, consisting of *`r colnames(instacart)`*. 

Each data illustrates a specific order, containing id of order, product, user, ailse and department. order_dow, order_hour_of_day, days_since_prior_order describe the order time. reorder=1 indicates this this product has been ordered by the user in the past.

```{r aisle}
aisle_uni <- instacart |> 
  pull(aisle) |> 
  unique()

aisle_order <- instacart |> 
  group_by(aisle) |> 
  summarize(
    orders = length(unique(order_id))
  ) |> 
  arrange(desc(orders))
```
In total there are *`r length(aisle_uni)`* aisles, the aisles with most items orderer is *`r aisle_order[1,1]`*

```{r aisle_plot}
aisle_order |> 
  filter(orders > 10000)|> 
  mutate(
    aisle = fct_reorder(aisle, orders) # order aisles with ascending order of order numbers
  ) |> 
  ggplot(aes(x = aisle, y = orders))+
  geom_bar(stat = "identity")+
  labs(
    title = "order numbers of each aisle"
  )+
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) # rotate x-axis labels
```

We can see from the plot that the top three ordered aisles are fresh fruits, fresh vegetables, packaged vegetables fruits.
```{r popluar_items}
items_order = instacart |> 
  filter(
    aisle %in% c("baking ingredients","dog food care","packaged vegetables fruits")
  ) |> 
  group_by(aisle, product_name) |> 
  summarise(
    orders = length(unique(order_id)) # calculate orders of each items
  ) |> 
  ungroup() |> 
  group_by(aisle) |> 
  arrange(desc(orders)) |> 
  slice_head(n = 3) # select items in each groups with top three orders

knitr::kable(items_order)
```

From the table, we can see that top three ordered items of packaged vegetables has much more orders than the others. 
```{r hour_of_the_day}
items_time <- instacart |> 
  filter(
    product_name %in% c("Pink Lady Apples","Coffee Ice Cream")
  ) |> 
  group_by(order_dow, product_name) |> 
  summarise(
    mean_hour = mean(order_hour_of_day)
  ) |> 
  pivot_wider(
    names_from = "product_name",
    values_from = "mean_hour"
  ) |> 
  round(digits = 2) |> 
  t()

knitr::kable(items_time[c(2,3),])
```
The table shows that Pink Lady Apples were usually purchased earlier than Coffee Ice Cream except Friday. The lag reaches longest on Thursday.

# Problem 2
```{r brfss_data}
data("brfss_smart2010") 

brfss_clean = brfss_smart2010 |> 
  janitor::clean_names() |> 
  filter(
    topic == "Overall Health",
    response %in% c("Excellent","Very good","Good","Fair","Poor")
  ) |> 
  mutate(
    response = fct_relevel(response, c("Poor","Fair","Good","Very good","Excellent"))
  ) |> 
  arrange(response)
```
This data described the Behavioral Risk Factors Surveillance System for Selected Metropolitan Area Risk Trends (SMART) for 2002-2010.

```{r states_over_7}
brfss_state7 = brfss_clean |> 
  group_by(year,locationabbr) |> 
  summarise(
    locaion_num = length(unique(locationdesc))
  )

brfss_state7_02 = brfss_state7 |> 
  filter(
    year == 2002,
    locaion_num >= 7
  )

brfss_state7_10 = brfss_state7 |> 
  filter(
    year == 2010,
    locaion_num >= 7
  )
```
The states with 7 or more observed locations in 2002 were `r brfss_state7_02 |> pull(locationabbr)`, and in 2010 were `r brfss_state7_10 |> pull(locationabbr)`
